%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}
%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------


\cvsubsection{Journal}
\begin{justify}
	\begin{itemize}[before=\fontsize{9pt}{1em}\bodyfontlight\upshape\color{text},leftmargin=3ex, nosep, noitemsep]
		\setlength{\parskip}{0pt}
		\renewcommand{\labelitemi}{\bullet}
		\item[J*]{\textbf{H. Zhang}, L. Jin, and C. Ye, “An RGB-D Camera based Visual Positioning System for Assistive Navigation by a Robotic Navigation Aid,” third round review by \emph{IEEE/CAA Journal of Automatica Sinica}, 2021.}
		\item[J1]{T. Shen, M. R. Afsar, \textbf{H. Zhang}, C. Ye, X. Shen, “A 3D Computer Vision-Guided Robotic Companion for Non-Contact Human Assistance and Rehabilitation,” \emph{Journal of Intelligent and Robotic Systems}, pp. 1-13, 2020.}
		\item[J2]{\textbf{H. Zhang} and C. Ye, “Plane-Aided Visual-Inertial Odometry for 6-DOF Pose Estimation of a Robotic Navigation Aid,” \emph{IEEE Access}, 2020. DOI: 10.1109/ACCESS.2020.2994299.}
		\item[J3]{L. Jin, \textbf{H. Zhang}, and C. Ye, “Camera Intrinsic Parameters Estimation by Visual Inertial Odometry for a Mobile Phone with Application to Assisted Navigation,” \emph{IEEE/ASME Transactions on Mechatronics}, 2020. DOI: 10.1109/TMECH.2020.2997606.}
		\item[J4]{\textbf{H. Zhang} and C. Ye, “An Indoor Wayfinding System based on Geometric Features Aided Graph SLAM for the Visually Impaired,” \emph{IEEE Transactions on Neural Systems and Rehabilitation Engineering}, vol. 25, no. 9, pp. 1592-1604, 2017.}
		\item[J5]{\textbf{H. Zhang} and C. Ye, “RGB-D Camera Based Walking Pattern Recognition by Support Vector Machines for a Smart Rollator,” \emph{International Journal of Intelligent Robotics and Applications}, vol. 1, no. 1, pp. 32-42, 2017.}
	\end{itemize}
\end{justify}

\cvsubsection{Conference} % \& Workshop

\begin{justify}
	\begin{itemize}[before=\fontsize{9pt}{1em}\bodyfontlight\upshape\color{text},leftmargin=3ex, nosep, noitemsep]
		\setlength{\parskip}{0pt}
		\renewcommand{\labelitemi}{\bullet}
		\item[C1]{\textbf{H. Zhang} and C. Ye, “DUI-VIO: Depth Uncertainty Incorporated Visual Inertial Odometry based on an RGB-D Camera,” in \emph{Proceedings of IEEE International Conference on Intelligent Robots and Systems (IROS)}, Las Vegas, Oct. 25-29, 2020.}
		\item[C2]{\textbf{H. Zhang}, L. Jin, and C. Ye, “The VCU-RVI Benchmark: Evaluating Visual Inertial Odometry for Indoor Navigation Applications with an RGB-D Camera,” in \emph{Proceedings of IEEE International Conference on Intelligent Robots and Systems (IROS)}, Las Vegas, Oct. 25-29, 2020.}	
		\item[C3]{L. Jin, \textbf{H. Zhang}, and C. Ye, “Human-Robot Interaction for Assisted Object Grasping by a Wearable Robotic Object Manipulation Aid for the Blind,” in \emph{Proceedings of 1st IEEE International Conference on Human-Machine Systems (ICHMS)}, Rome (Virtual), Sep. 7-9, 2020. }
		\item[C4]{\textbf{H. Zhang} and C. Ye, “A Visual Positioning System for Indoor Blind Navigation,” in \emph{Proceedings of IEEE International Conference on Robotics and Automation (ICRA)}, Paris (Virtual), May 31-June 4, 2020.}
		\item[C5]{\textbf{H. Zhang} and C. Ye, “Human-Robot Interaction for Assisted Wayfinding of a Robotic Navigation Aid for the Blind,” in \emph{12th IEEE Conference on Human System Interaction (HSI)}, Richmond, Virginia, June 25-27, 2019, pp. 137-142.(\textbf{Best Conference Paper Award})}
		\item[C6]{\textbf{H. Zhang}, L. Jin, Hao Zhang, C. Ye, “A Comparative Analysis of Visual-Inertial SLAM for Assisted Wayfinding of the Visually Impaired,” in \emph{IEEE Winter Conference on Applications of Computer Vision (WACV)}, Hawaii, Jan. 7-11, 2019, pp. 210-217.}
		\item[C7]{X. Liu, \textbf{H. Zhang}, L. Jin, C. Ye,  “A Wearable Robotic Object Manipulation Aid for the Visually Impaired,” in \emph{1st IEEE International Conference on Micro/Nano Sensors for AI, Healthcare, and Robotics (NSENS)}, Shenzhen, China, Dec. 5-7, 2018, pp. 5-9.}
		\item[C8]{T. Shen, M. R. Afsar, \textbf{H. Zhang}, C. Ye, X. Shen, “Development of a Motorized Robotic Walker Guided by an Image Processing System for Human Walking Assistance and Rehabilitation,” in \emph{Proceedings of the ASME Dynamic Systems and Control Conference (DSCC)}, Atlanta, Georgia, Sep. 30-Oct. 3, 2018, Vol. 51890, p. V001T07A009.}
		\item[C9]{M. R. Afsar1, M. Wadsworth, T. Shen, \textbf{H. Zhang}, C. Ye, X. Shen , “A Motorized Robotic Walker for Human Walking Assistance,” in \emph{ASME Dynamic Systems and Control Conference}, Minneapolis, Minnesota, April 10–13, 2017, Vol. 40672, p. V001T05A013.}
		\item[C10]{\textbf{H. Zhang} and C. Ye, “Plane-Aided Visual-Inertial Odometry for Pose Estimation of a 3D Camera based Indoor Blind Navigation,” in \emph{Proceedings of British Machine Vision Conference (BMVC)}, London, Sep. 4-7, 2017.}
		\item[C11]{\textbf{H. Zhang} and C. Ye, “An Indoor navigation aid for the visually impaired,” in \emph{IEEE International Conference on Robotics and Biomimetics (ROBIO)}, Qingdao, China, Dec. 3-7, 2016, pp. 467-472. (\textbf{Finalist of Best Conference Paper Award})}
		\item[C12]{\textbf{H. Zhang} and C. Ye, “An RGB-D Camera based Walking Pattern Detection Method for Smart Rollators,” in \emph{Proceedings of the 11th International Symposium on Visual Computing (ISVC)}, Las Vegas, Dec. 14-16, 2015, pp. 624-633.}
		\item[C13]{\textbf{H. Zhang}, Z. Hou, N. Li, S, Song, P. Xu, “Duo-Graph: An Efficient and Robust Method for Large-scale Mapping for Visual-Guided Robots,” in \emph{12th International Conference on Control, Automation, Robotics and Vision (ICARCV)}, Guangzhou, China, Dec. 5-7, 2012, pp. 323-328.}
		\item[C14]{\textbf{H. Zhang}, Z. Hou, N. Li, S. Song, “A Graph-based Hierarchical SLAM Framework for Large-scale Mapping,” in \emph{5th International Conference on Intelligent Robotics and Applications (ICIRA)}, Montreal, Quebec, Oct. 3-5, 2012, vol. 7507, pp 439-448.}
	\end{itemize}
\end{justify}


\cvsubsection{Workshop}
\begin{justify}
	\begin{itemize}[before=\fontsize{9pt}{1em}\bodyfontlight\upshape\color{text},leftmargin=3ex, nosep, noitemsep]
		\setlength{\parskip}{0pt}
		\renewcommand{\labelitemi}{\bullet}
		\item[W1]{\textbf{H. Zhang}, L. Jin, and C. Ye, “A depth-enhanced visual inertial odometry for a robotic navigation aid for blind people,” in \emph{Proceedings Visual-Inertial Navigation: Challenges and Applications Workshop at IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}, Macau, China, Nov. 4-8, 2019. (\textbf{LORD Best Paper Award})}
		\item[W2]{\textbf{H. Zhang}, G. Liu and Z. Hou, “An Iterative Graph Optimization Approach for 2D SLAM,” in \emph{ 6th IROS Workshop on Planning, Perception and Navigation for Intelligent Vehicles (PPNIV)}, Chicago, Sep. 14-18, 2014.}
	\end{itemize}
\end{justify}


